### 2015-02-14 paper_10_intro.tex
working on SQL

    After the proper tools are in place to collect the necessary
    data on software development and software analytics are being
    properly implemented, an obvious next step is the
    application of gamification to software development. Gamification
    is ``the process of making activities more game-like'' \cite{Werbach2014}.
    Some of the benefits of gamification are higher productivity, competition,
    and greater enjoyment.  
    Prior attempts
    at gamification of software development focus only on 
    the computer programming phase \cite{Snipes2013}. Others
    focus on defining a framework for gamification within
    the software development process \cite{Jain2013}. There are 
    even some indications that gamification might help increase
    software quality \cite{Dubois2013}. 
    While this work will not focus on gamification, it is important to note
    that an implementation of an evaluation technique for software
    development could be implemented simultaneously with a gamification
    strategy. Both will require new collections of data and new reporting.

>>>>

    After the proper tools are in place to collect the necessary
    data on software development and software analytics are being
    p roperly implemented, an obvious next step is the
    application of gamification to software development. Gamification
    is ``the process of making activities more game-like'' \cite{Werbach2014}.
    Some of the benefits of gamification are higher productivity, competition,
    and greater enjoyment.  
    Prior attempts
    at gamification of software development focus only on 
    the computer programming phase \cite{Snipes2013}. Others
    focus on defining a framework for gamification within
    the software development process \cite{Jain2013}. There are 
    even some indications that gamification might help increase
    software quality \cite{Dubois2013}. 
    While this work will not focus on gamification, it is important to note
    that an implementation of an evaluation technique for software
    development could be implemented simultaneously with a gamification
    strategy. Both will require new collections of data and new reporting.
